### 2022-05-21 Publish Paper/manuscript_main.tex
Update publish paper

\begin{table}

@@

@@

\begin{figure}

@@

\subsection{Backbone Model Architecture}
In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\begin{table}
	\centering
	\begin{tabular}{|c | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
\caption{Size and Parameters and Depth of backbone model used in this paper}
\label{table:2}
\end{table}

@@

All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. The accuracy of all model is presented in the figure below:\\

@@

@@

\end{table}\\

@@

As the results, metadata does not make the model more balanced and improve the model performance. The reason why the model become much more balanced is the weighted loss function. Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. Therefore, DenseNet201, InceptionResNetV2 trained with weighted loss function have recall in akiec of $0.85$. $0.82$, respectively, as opposed to their training in akiec without weighted loss function. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately. 

@@

\end{table}\\

@@

\end{table}\\

@@

\end{table}\\
Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. The table 8 illustrates the deeper analyzing of the three models. It's clear that MobileNetV3Large and NasNetMobile are the two best performance model. Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.\\
\begin{table}

@@

		Model & MobileNetV2 & MobileNetV3Small & MobileNetV3Large & NasNetMobile\\

@@

At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.
\begin{table}

@@

		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 

>>>>

\FloatBarrier
\begin{table}[ht]

@@

\FloatBarrier

@@

@@

\subsection{Backbone Model Architecture}
In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\FloatBarrier
\begin{table}[ht]
	\begin{tabular}{|c | c c c|} 
		Model & Size(MB) & Parameters & Depth \\ 
		Resnet50 & 98 & 25.6M & 107 \\ 
		Resnet152 & 232 & 60.4M & 311 \\ 
		DenseNet201 & 80 & 20.2M & 402 \\
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		MobileNet & 16 & 4.3M & 55 \\ 
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		NasnetMobile & 23 & 5.3M & 308 \\
		NasnetLarge & 343 & 88.9M & 533 \\ 
\caption{Size and Parameters and Depth of backbone model used in this paper}
\label{table:2}
\FloatBarrier

@@

All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. The accuracy of all model is presented in the figure below:
\FloatBarrier

@@

\FloatBarrier
\FloatBarrier

@@

\FloatBarrier

@@

As the results, metadata does make the model less imbalanced and improve the model performance by reducing the amount of data needed for achieving nearly the expected results.On the other hand, the reason why the model become much more balanced is the weighted loss function. Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. Therefore, DenseNet201, InceptionResNetV2 trained with weighted loss function have recall in akiec of $0.85$. $0.82$, respectively, as opposed to their training in akiec without weighted loss function. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.\\ 
\FloatBarrier

@@

\FloatBarrier
\FloatBarrier

@@

\FloatBarrier
\FloatBarrier
\begin{table}[ht]

@@

\FloatBarrier
Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. The table 8 illustrates the deeper analyzing of the three models. It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
\FloatBarrier
\begin{table}[ht]

@@

		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\

@@

\FloatBarrier
Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2. Therefore, at the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.
\FloatBarrier
\begin{table}[ht]

@@

		MobileNetV3Large-Layer[:230] + Soft-Attention & s0.85 \\ 

### 2022-05-21 Publish Paper/manuscript_title_etc.tex
Update
Update publish paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Nowadays, the dramatic development of the big city and industrial field leads to a higher rate of skin disease because of polluted air. Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient. They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification. After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning. In Deep Learning, they often use transfer learning. Some new approaches are GradCam, Kernel Shap, Student and Teacher model. In Machine Learning, Random Forest, and Support Vector Machine are applied. The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer. The soft-Attention layer is tested in a previous paper that improve the model performance. I also try some other combinations to construct an optimized model that can use on mobile phone. After the experiment process, I found out that metadata makes the performance of the model more balanced than in the previous paper. I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with a bit lower accuracy but thirty times as fast as other combinations.
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{Balanced and Optimized Skin Cancer Classification Model using Soft Attention and Metadata}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Nowadays, the dramatic development of the big city and industrial field leads to a higher rate of skin disease because of polluted air. Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient. They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification. After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning. In Deep Learning, they often use transfer learning. Some new approaches are GradCam, Kernel Shap, Student and Teacher model. In Machine Learning, Random Forest, and Support Vector Machine are applied. The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer. The soft-Attention layer is tested in a previous paper that improve the model performance to 92 percent accuracy. I also try some other combinations to construct an optimized model that can use on mobile phone. After the experiment process, I found out that metadata and weighted loss function makes the performance of the model less imbalanced with 90 percent accuracy but its f1-score and recall score standard deviation is 0.08 and 0.09, respectively. I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with 86 percent accuracy but thirty times as fast as the highest performance model.
}
